What Can Stack Traces Tell us about Exceptions in Java?

### 2014-07-07 android-stacks.tex
even more changes on Introduction

Bug issues have called the attention of researhc community and  have been the target of several 
researches [][][]. A subtype of a bug issue are the ones related to system 
crashes, also called crash reports such reports can be automatically generated 
as the system crashes or can be manually reported by developers/users [complete]...

@@

Modern applications have to cope with similar and increasing number of sources of failures
 that arise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware.   The exception handling 
mechanism~\cite{goodenough1975exception}, been embedded in several 
programming languages (e.g. Java, C++, C\#), is one of the most used
 schemes for detecting and recovering from such failures.

Such exception stack traces are a useful source of 
information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.

However existing research has focused on the analysis of a 
single system at a time. Moreover, the search facilities of repositories are very limited, also
enabling the analysis of a single project.

>>>>

Bug issues have called the attention of research community and have been the target of several 
researches [][][]. A subtype of a bug issue are the ones related to system 
crashes, also called crash reports such reports can be automatically generated 
as the system crashes or can be manually reported by developers/users [complete]...

@@

Such failure stack traces are a useful source of 
information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.

The exception handling mechanism~\cite{goodenough1975exception},
 is one of the most used schemes for detecting and recovering from such 
failures. Exceptions may arrise as a consequence of faults in the application
itself (e.g., access of null references), noisy user inputs or faults in
underlying middleware or hardware.

Although moder application have to deal with a similar and increasing number of 
source of failures, existing research has focused on the analysis of a 
single system at a time.
